\documentclass{homework}
\begin{document}
\section{Filtered Sentences}
%Organize, in a schematic way, the information that can be extracted from the Natural Language Sentences

The owner of a bookstore needs an online platform to sell and check his books. he wants to easily track profits, sales graph and daily to annual sales.\\

The system will manage \textbf{four} different \textbf{user} roles:
\begin{itemize}
    \item \textbf{Owner}: is the legal owner of the company and the site. 
     -Identified by e-mail and password.
	can access all the information about the books.
	can access the database updates.
	can access to sales tables like monthly sales,annual sales etc.

    \item \textbf{Warehouse}: Employees of the company. They can add new books to the system, update the data of the existing book, and keep track of stock.
        -Identified by name, surname, id, email,password and department
	can access all data about books
	can add new data
	can edit data

    \item \textbf{Customer}: can access book’s information and buy books.
         -Idefined by name, surname, e-mail, password, telephone number, address and card information.
	can access to book stocks
	can access all the data of books
	can search for authors, publisher etc.
	can create an order
  \item \textbf{Sales }: Other employees of the bookstore 
-Identified by name, surname, id,password, email, department
Receive the order from customersCreate the reports of purrchases 
Can access all the information about books
Can access inventory
Can receive the order from customers
Can access data of the customers
\item \textbf{Inventory}: 
   -Report which is written by Warehouse department team regarding the books which are still in the warehouse. 
Can be accessed by Owner and Sales
 \item \textbf{Reports}: 
      -It is prepared by employees using sales data. Visualization of monthly, annual sales figures, which category sells more, etc. 
Can be accessed by Owner.

\end{itemize}


\noindent The customer can buy one or more \textbf{books}. A \textbf{book};
\begin{itemize}
    \item  - identified by bookID, title, author, language, publisher, number of pages, price,quantity of books, categories of book.
    \end{itemize}
\noindent 
 Owner ,employees and customer have access to all book information.
\end{document}
