\section{Natural Language Sentences}
%what did we discover during the interviews? what characteristic should the system have?

Since nowadays everyone is using internet, every business is trying to take the opportunities that  
internet offers. Even bookstores that have been selling books in traditional ways for decades are now 
attempting to sell them "online". This transition is not very easy to happen, because in the background 
they should have the best database and the best application in order to help them to track everything 
they need and manage their operations as smoothly as possible. This goal pushed us to create an 
application which will help each of its users to reach their demands. The main objectives of this 
application will be:
\begin{itemize}
    \item To help the owner (The director) of the bookstore to run his business as easier as possible. He will be able to read the profits and the reports that he needs, which will be created by his employees.
    \item Helping the employees of the bookstore (sales, warehouse department) to create their reports and give them all the necessary permissions to properly perform their job.
    \item To give the customers the opportunity to check the books that the bookstore offers and order them online. 
\end{itemize}
Regarding the most important part of the bookstore which are books the application will store the necessary information for each book in the database. Some of the data stored for books will include:
\begin{itemize}
\item BookID
\item Title
\item Author
\item Publisher
\item Price
\item Quantity (of the books)
\item Number of pages
\item Language
\item Category of the book
\item Etc
\end{itemize}
Since books will have information about author, publisher and language, it will be easier for the customers to find the books of their favorite author or publisher and the language they need.
 All the information about the books will be inserted by Warehouse Department, they will be responsible for the information regarding the books and also on updating the inventories of the warehouse. Sales on the other hand will manage the orders that each customer makes. Their responsibility is to properly create the right “orderline” based on customers’ requirements and create the reports required by the owner. Sales also can do discounts for different 	orders. All the employees will be identified by their names, surname, id, emails and the departments where they work.

 Customers can use this application only by registering first. It will be required for them to set some information for example:
 \begin{itemize}
\item Name
\item Surname
\item Telephone number
\item e-mail
\item Etc
 \end{itemize}
These requirements will assist the sales team in properly creating their reports. To ensure that orders will be delivered to the correct address the client should also set the address where he needs his order to be delivered. All the customers will be able to see all the information about books. 